The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-10 paper/ms.tex
add amalie to authors
init red clump star section
remove newpage
new sections

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6,7}$
Timothy R. White,$^{5,8}$\newauthor
Daniel Huber,$^{9,10,11}$
Ashley Chontos,$^{9}$
Victor Silva Aguirre,$^{5}$
Victoria Antoci,$^{5}$\newauthor
Suzanne Aigrain,$^{3}$ 
Timothy R. Bedding,$^{10,5}$
Jie Yu,$^{10,5}$ and friends
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA\\
$^{8}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{9}$Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{10}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA
}

@@

Beyond searching for planets, \kepler has revolutionized the field of asteroseismology \citep{2010PASP..122..131G}. It has yielded the first detection of gravity-mode period spacings in a red giant \citep{rggmodes}, enabling probes of interior rotation of red giants \citep{rggmoderotation} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium}. It has also permitted the determination of ages and fundamental parameters of main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence. \newpage

@@

\subsection{Chemical Composition}
place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from. May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys

\subsection{Other Stars}
\label{other}

\subsection{Classical Pulsators}

@@

>>>>

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6,7}$
Timothy R. White,$^{5,8}$\newauthor
Daniel Huber,$^{9,10,11}$
Ashley Chontos,$^{9}$
Victor Silva Aguirre,$^{5}$
Victoria Antoci,$^{5}$\newauthor
Suzanne Aigrain,$^{3}$ 
Timothy R. Bedding,$^{10,5}$
Jie Yu,$^{10,5}$ 
Amalie Stokholm,$^{5}$\newauthor
and friends
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA\\
$^{8}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{9}$Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{10}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA
}

@@

Beyond searching for planets, \kepler has revolutionized the field of asteroseismology \citep{2010PASP..122..131G}. It has yielded the first detection of gravity-mode period spacings in a red giant \citep{rggmodes}, enabling probes of interior rotation of red giants \citep{rggmoderotation} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium}. It has also permitted the determination of ages and fundamental parameters of main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence.

@@

\subsection{Chemical Composition}
\label{chemical}
place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from. May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys

\subsection{Red Clump Stars}
\label{clumpstars}

From visual inspection of the power spectra, HD 181069, HD 183124, HD 182354, HD 182692, and HD 180658 are seen to be core helium-burning red clump stars.

\subsection{Classical Pulsators}
\label{pulsators}

@@

\subsection{Eclipsing Binaries}
\label{ebs}
